Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-02 robdml.tex
tex

After validating the effectiveness of our proposed method, we conduct
experiments on CUB, CARS and SOP to compare our proposed method
with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
and ACT~\cite{robrank}, as shown in \cref{tab:sota}.

According to the results, EST[$\mathcal{R}$] achieves a relatively high
R@1 when $\eta=8$,

>>>>

After validating the effectiveness of our proposed method, we conduct
experiments on CUB, CARS and SOP to compare our proposed method
with the state-of-the-art defense methods, \ie, EST~\cite{advrank}
and ACT~\cite{robrank}, as shown in \cref{tab:sota}.
%
An ideal defense method should be able to achieve a high ERS, a high R@1,
as well as a high efficiency (\ie, being able to gain higher robustness
under a fixed training cost).

According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
increased to $32$.
%
Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
settings compared to other methods.
%
Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
in even lower ERS based on the observations in previous subsections, and
EST has been greatly outperformed by ACT~\cite{robrank}.
